Instructions for ACL 2020 Proceedings

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
add to related work & background references

\section{Related work} % add references first
%  - BERT domain transfer
%  - BERT/LM for DAR

@@

\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)

@@

\section{Discussion} % add items to discuss

\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}

>>>>

References
\begin{itemize}
  \item \citet{austinHowThingsWords2009} -- speeh acts
  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
\end{itemize}

\section{Related work} % add references first
Dialogue act recoginition
\begin{itemize}
  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models. Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
\end{itemize}

Pre-training/transfer learning for dialogue
\begin{itemize}
  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
\end{itemize}

@@

\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
\begin{itemize}
  \item Setup
    \begin{itemize}
      \item we do additional pre-training for the BERT encoder on in-domain data
      \item note: this is sometimes referred to as fine-tuning, but we reserve that term for task-specific training of the encoder model

      \item SWDA/AMI (excluding dialogues in the DAR test set)
      \item 10 epoch AMI / 10 epochs SWBD / 5 epochs of each
    \end{itemize}
\end{itemize}

@@

\section{Discussion} % add items to discuss
\begin{itemize}
  \item RoBERTa training scheme finds that next sentence prediction is of little importance. Is this true for us too? (suspect not due to discourse importance). see: https://github.com/huggingface/transformers/issues/1622
\end{itemize}

\bibliography{acl2020}
\bibliographystyle{acl_natbib}
